Dendrochronological dates confirm a Late Prehistoric population decline in the American Southwest derived from radiocarbon dates

### 2020-04-17 analysis/robinson2020.Rmd
bumping to r 3.6.3 in dockerfile

Our final dataset includes `r nrow(all_data$Radiocarbon) %>% format(big.mark = ',')` radiocarbon dates from `r all_data$Radiocarbon$SiteID %>% unique() %>% length %>% format(big.mark = ',')` unique sites, dating from `r max(all_data$Radiocarbon$Date_BP)`--`r min(all_data$Radiocarbon$Date_BP)` BP (uncalibrated; `r -1 * (1950 - max(all_data$Radiocarbon$Date_BP)) - 1` BC--`r 1950 - min(all_data$Radiocarbon$Date_BP)` AD) and `r nrow(all_data[['Tree-ring']]) %>% format(big.mark = ',')` tree-ring dates from `r all_data[["Tree-ring"]]$SiteID %>% unique() %>% length %>% format(big.mark = ',')` unique sites, dating from `r max(all_data[['Tree-ring']]$Date_BP)` -- `r min(all_data[['Tree-ring']]$Date_BP)` BP (`r 1950 - max(all_data[['Tree-ring']]$Date_BP)`--`r 1950 - min(all_data[['Tree-ring']]$Date_BP)` AD). Table \@ref(tab:Table1) presents the counts of dates and sites of each date type in the CMV and NRG study areas.

@@

>>>>

Our final dataset includes `r nrow(all_data$Radiocarbon) %>% format(big.mark = ',')` radiocarbon dates from `r all_data$Radiocarbon$SiteID %>% unique() %>% length %>% format(big.mark = ',')` unique sites, dating from `r max(all_data$Radiocarbon$Date_BP)`--`r min(all_data$Radiocarbon$Date_BP)` BP (uncalibrated; `r -1 * (1950 - max(all_data$Radiocarbon$Date_BP)) - 1` BC--`r 1950 - min(all_data$Radiocarbon$Date_BP)` AD) and `r nrow(all_data[['Tree-ring']]) %>% format(big.mark = ',')` tree-ring dates from `r all_data[["Tree-ring"]]$SiteID %>% unique() %>% length %>% format(big.mark = ',')` unique sites, dating from `r max(all_data[['Tree-ring']]$Date_BP)`--`r min(all_data[['Tree-ring']]$Date_BP)` BP (`r 1950 - max(all_data[['Tree-ring']]$Date_BP)`--`r 1950 - min(all_data[['Tree-ring']]$Date_BP)` AD). Table \@ref(tab:Table1) presents the counts of dates and sites of each date type in the CMV and NRG study areas.

@@

rm(radiocarbon_spd, dendro_spd)
gc()
gc()

### 2020-04-17 analysis/robinson2020.tex
bumping to r 3.6.3 in dockerfile

Our final dataset includes 1,531 radiocarbon dates from 482 unique sites, dating from 2260--90 BP (uncalibrated; 309 BC--1860 AD) and 15,077 tree-ring dates from 770 unique sites, dating from 1749 -- 152 BP (201--1798 AD). Table \ref{tab:Table1} presents the counts of dates and sites of each date type in the CMV and NRG study areas.

@@

This report is part of a research compendium developed using the \texttt{rrtools} package for reproducible research (Marwick, \protect\hyperlink{ref-rrtools}{2019}, \protect\hyperlink{ref-Marwick2017}{2017}). This report was generated on 2020-04-17 07:45:54 using the following computational environment and dependencies:

>>>>

Our final dataset includes 1,531 radiocarbon dates from 482 unique sites, dating from 2260--90 BP (uncalibrated; 309 BC--1860 AD) and 15,077 tree-ring dates from 770 unique sites, dating from 1749--152 BP (201--1798 AD). Table \ref{tab:Table1} presents the counts of dates and sites of each date type in the CMV and NRG study areas.

@@

This report is part of a research compendium developed using the \texttt{rrtools} package for reproducible research (Marwick, \protect\hyperlink{ref-rrtools}{2019}, \protect\hyperlink{ref-Marwick2017}{2017}). This report was generated on 2020-04-17 08:14:58 using the following computational environment and dependencies:
